Robotic Cart System

### 2020-10-06 systemLevelFunctionalRequirements.tex
Moved block diagram and added to document
Update systemLevelFunctionalRequirements.tex
Updated systemLevelFunctionalRequirements System Block Diagram Section

%------------------------------------------------
\section{System Architecture}
\subsection{System Block Diagram}
The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device. \textlangle Darrah's block description here\textrangle

A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=6.5in]{figs/img/sysBlockDiag}
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
\end{figure}

>>>>

%------------------------------------------------
\section{System Architecture}
\subsection{System Block Diagram}
The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device. The system, as a whole, will take into consideration of the world around it and avoid obstacles while trying to follow the remote target.  The system will also be trying to follow the remote pointer even if it loses the line of site detection.  If the robot loses track or falls to far behind the remote the remote will indicate this to the user.

A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
\begin{figure}[b]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=6.5in]{figs/system_block_diagram}
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
\end{figure}
